---
title: "Write Up Linear Model"
author: "Dom Ciriello"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 



You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)


```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```


# Numerical results

```{r}
cor(SIMS~ARM,data=data)
``` 
# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
This adjusted R-squared is the second smallest of the 3 models. This means it has the second least amount of correction, which makes it more accurate than model 2 but less accurate than model 3.

```{r}
newdata=data.frame(GRIP=94, ARM=88)
predict(model.1,newdata,interval="prediction")
```


# now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

The equation for SIMS explained by ARM is:
SIMS=-4.1+.055*ARM

```{r}
basicGG <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicGG + geom_point()
```


# Numerical results

```{r}
cor(SIMS~GRIP,data=data)
``` 
# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2,newdata,interval="prediction")
```

This model has the smallest Adjusted R-squared value. This means that it has the smallest amount of correction and is the least accurate model out of the 3 we made.

# now add the model fit to our plot
  







# Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3,newdata,interval="prediction")
```
SIMS=-5.43+.037 * ARM + .024 * GRIP

This model has the highest Adjusted R-squared value. It performed the most correction and produced the most accurate model out of the 3 models we created.

```{r}
anova(model.1, model.3)
```

We reject the null hypothesis because the P-value is extremely small (.000005) and we conclude that the best model for predicting the sims is model 3. This anova shows that model 3 changed/fixed it by 29.45.